Homework 3

### 2019-10-02 hw3/MSimonsHW3.tex
Hw3 number 4

\item

>>>>

\item Assume $a$, $b$ are elements in $R_1 \cap R_2$.  This implies $a$, $b$ are
in $R_1$.  Since $R_1$ is a subring, $a+b$ is in $R_1$.  Similarly, $a$, $b$ are
in $R_2$ and $a+b$ is in $R_2$ as $R_2$ is also a subring.  Since $a+b$ is in
$R_1$ and $R_2$, $a+b$ is in $R_1 \cap R_2$ and $R_1 \cap R_2$ is closed
under addition.
\\
\\
Since $R_1$ and $R_2$ are subrings, $ab$ is in $R_1$ and $ab$ is in $R_2$.
Therefore $ab$ is in $R_1 \cap R_2$ and $R_1 \cap R_2$ is closed under
multiplication.
\\
\\
Thus, $R_1 \cap R_2$ is a subring of $R$ (and therefore a ring).
\\
\\
$R_1 \cup R_2$ is not necessarily a ring.  Let $R_1$ and $R_2$ be
 subrings of $R$ such that $R_2$ is not a subring of $R_1$.  Let $a$ be an
 element of $R_1$, but not of $R_2$.  Let $b$ be any element of $R_2$.
 \\
 \\
 If $R_1 \cup R_2$ is a ring, $a+b$ is in $R_1 \cup R_2$.  By definition of
 union, $a+b$ is in $R_1$ or $a+b$ is in $R_2$.  If $a+b$ is in $R_1$, then
 $(a+b)-a$ is also in $R_1$ (since $R_1$ is closed under addition).  However,
 this implies $b$ is in $R_1$.  If any element in $R_2$ is an element of $R_1$,
 then $R_2$ is a subring of $R_1$, which is a contradiction.  If $a+b$ is in
 $R_2$, then $(a+b)-b$ is also in $R_2$.  This implies that $a$ is in $R_2$,
 which is another contradiction.  Therefore, if two subrings exist such that
 neither is a subset of the other, their union is not a ring.
